---
output: 
  github_document
---

## Inferring wildlife population trends from hierarchical habitat selection: a case study with boreal caribou

[![DOI](https://zenodo.org/badge/375803485.svg)](https://doi.org/10.5281/zenodo.15750844)

* Authors:
    + [Julie W. Turner](https://www.julwturner.com)
    + Samuel Haché 
    + James Hodson 
    + Philip D. McLoughlin 
    + Tatiane Micheletti
    + Michael J. L. Peers
    + Agnès Pelletier
    + Eliot McIntire 

    

This repository contains the data and code accompanying the paper "Inferring wildlife population trends from hierarchical habitat selection: a case study with boreal caribou". 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

libs <- c('data.table', 'knitr', 'tidyr')
lapply(libs, require, character.only = TRUE)

## Input data ----
derivedPath <- file.path('data_pub', 'derived-data')

metadat <- fread(file.path(derivedPath, 'data_description.csv'))

```

## Data
Data processing and harmonizing occurred in scripts 1-5. Data included here are the aspatial, calculated movement parameters (steps and turn angles) and extracted covariates for each step used in analyses (scripts 6-9). Descriptions of the variables in the data for analysis are below.

```{r summary, echo=FALSE}

kable(metadat, options = list(pageLength = 35))
```
